---
title: "Gemma LMM Summary"
output:
  html_document:
    toc: yes
---

```{r, echo=FALSE}
library(knitr)
library(qqman)

rawout <- "output"
p.threshold <- 0.01
p.maxsel <- 500
p.adj.m <- c("bonferroni", "holm", "hochberg", "fdr", "BY")
```

The following considerations were used in this document:  
1) Resuls are based on __centralized__ distance matrix only, because it generally shows better PVE and doesn't cheange the results on GWAS.  
2) p-values for likelihood ratio test are used for reporting. Other tests are asymptotically equivalent to LRT.  
3) The following methods used for p-values correction: `r p.adj.m`  

```{r include=FALSE, message=FALSE, warning=FALSE}

b <- "D:\\work\\bio\\roma_13-march-2015\\gemma_out"
dataset <- "Dataset_9-2ndLineNonInj_bin"
rawout <- file.path(rawout, dataset)

if(!file.exists(rawout)) dir.create(rawout, recursive = TRUE)
b <- file.path(b, dataset)

med.f <- function(base_dir, drug) {
  file.path(base_dir, drug, sprintf("%s-lmm.c.assoc.txt", drug))
}

c.entr <- function(drug) list(d = drug, f = med.f(b, drug))

dirs <- list.dirs(b, full.names = FALSE, recursive = FALSE)
input <- lapply(dirs, c.entr)

out <- NULL
for (i in input) {
  description <- i$d
  path <- i$f
  out <- c(out, knit_child('summary-tile.rmd'))
}
```

`r paste(out, collapse='\n')`