---
title: "Gemma LMM Summary"
output:
  html_document:
    toc: yes
---

```{r echo=FALSE, include=FALSE}
library(knitr)
library(qqman)
library(ggplot2)

scriptdir <- "D:\\work\\bio\\rlib\\common"
source(file.path(scriptdir, "config.R"))

source(lib.reader)
source(lib.summary)

# override defaults
remove.dups <- TRUE
maf.thresh <- NA # let GEMMA calculate it for us

pheno.pos <- "2"
pheno.neg <- "1"

p.threshold <- 0.01
p.maxsel <- 100
p.adj.m <- c("bonferroni", "holm", "hochberg", "fdr", "BY")
```

The following considerations were used in this document:  
1) Resuls are based on __centralized__ distance matrix only, because it generally shows better PVE and doesn't cheange the results on GWAS.  
2) p-values for likelihood ratio test are used for reporting. Other tests are asymptotically equivalent to LRT.  
3) The following methods used for p-values correction: `r p.adj.m`  

```{r include=FALSE, message=FALSE, warning=FALSE}
out <- NULL
for (dataset.dir in func.filter.datadir(home.gemma)) {
  dataset.basename <- basename(dataset.dir)
  dataset.name <- sub("^(dataset_[.0-9]+).*", "\\1", dataset.basename)
  plink.files <- file.path(base, dataset.name)
  file_pattern <- func.plink.filename(plink.files)
  
  pheno.desc <- read.phenotype.ordering(plink.files)
  
  plink.data <- read.snps.plink.binary(plink.files, 
                                       file_pattern, 
                                       pheno.desc, 
                                       use.phe = phe.as.fam, 
                                       remove.dups = remove.dups,
                                       maf.threshold = maf.thresh)
  
  X <- plink.data$X
  data.m.nona <- plink.data$d
  data.p <- plink.data$p
  out <- c(out, knit_child('summary-dataset.rmd'))
}
```

`r paste(out, collapse='\n')`