```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
medicine <- colnames(tM)[1]

clPheno <- merge(tM, data.m.nona, all = FALSE, by = "row.names")

X <- as.matrix(clPheno[,3:ncol(clPheno)])
y <- clPheno[,2]
y.r <- as.integer(y)
y.r.min <- min(y.r)
y.r.max <- max(y.r)

fit.regularized <- cv.glmnet(X, y, family = "binomial", alpha = 0.7, lambda = seq(1, 0, by = -0.02))
lambda.best <- fit.regularized$lambda.min

last.pos <- as.integer(colnames(X)[ncol(X)])

calc.set.diff <- function(set1, set2, antisimmetric = FALSE) {
  dist.matrix <- abs(outer(set1, set2, FUN = "-"))
  components <- NULL
  if(antisimmetric) {
    components <- apply(dist.matrix, 1, min)
  } else {
    components <- c(apply(dist.matrix, 2, min), apply(dist.matrix, 1, min))
  }
  mean(components)
}

bound.foo <- function(data) {
  ps.sorted <- sort(data)
  ps.bound <- ps.sorted[min(length(ps.sorted), emma.sample)]
  min(emma.bound, ps.bound)
}
```

# '`r medicine`' Details

## Known mutations (Relative to H37Rv)

```{r, warning=FALSE}
known.snps <- known.mutations[[medicine]]
known.snps
```

## Elastic Net for Best Lambda

Lambda that minimizes CV error

```{r, warning=FALSE}
best.pos <- which(fit.regularized$lambda == lambda.best)

lambda.best
```

Corresponding error

```{r, warning=FALSE}
fit.regularized$cvm[best.pos]
```

Test error

```{r, warning=FALSE}
p <- predict(fit.regularized, X, s = lambda.best)[,1]
sum(ifelse(p < 0, y.r.min, y.r.max) != y.r) / ifelse(length(p), length(p), 1)
```

Number of nonzero coefficients (all non-zero)

```{r, warning=FALSE}
fit.regularized$nzero[best.pos]
```

Nonzero coefficients*:

```{r, results='asis', warning=FALSE}
model.coef <- coef(fit.regularized, s = lambda.best)
model.coef.nointerc <- model.coef[2:length(model.coef)]
act.idx <- which(abs(model.coef.nointerc) > sign.bound)

act.snps <- as.integer(colnames(X)[act.idx])
act.coef <- model.coef.nointerc[act.idx]
s.f <- data.frame(position = act.idx, bp = act.snps, coeficient = act.coef)

write.csv(s.f, file = paste0(medicine, ".lm.csv"))
kable(s.f)
```

Reduced model test error*

```{r, warning=FALSE}
if(length(act.idx) > 0) {
  X.reduced <- X[,act.idx]
  fit.reduced <- cv.glmnet(X.reduced, y, family = "binomial", lambda = seq(1, 0, by = -0.02))
  Y.predicted <- predict(fit.reduced, X.reduced, s = fit.reduced$lambda.min)
  sum((Y.predicted < 0) != y.r) / ifelse(length(Y.predicted), length(Y.predicted), 1)
}
```

Average minimum distance between known mutations and discovered

```{r, warning=FALSE}
if(!is.null(known.snps)) {
  calc.set.diff(known.snps, act.snps)
}
```

* - all coefficients <= `r sign.bound` were filtered

## Charts

Known mutations (H37Rv):

```{r, warning=FALSE}
if(!is.null(known.snps)) {
  plot(known.snps, rep(1, length(known.snps)), xlim = c(1, last.pos))
}
```

Nonzero coefficients (LASSO):

```{r, warning=FALSE}
if(nrow(s.f) > 0) {
  plot(s.f$bp, s.f$coeficient, 
     xlim = c(1, last.pos), xlab = "SNP index", ylab = "coeficient")
} else {
  "Not Available"
}
```

